---
output: html_document
editor_options: 
  chunk_output_type: console
---

## Outcomes

```{r message=FALSE}
p1 <- estimate_density(df$Confidence, at=df$Participant, method = "kernSmooth") |> 
  ggplot(aes(x=x, y=y)) +
  geom_line(aes(color = Group)) + 
  scale_x_continuous(labels = scales::percent, expand = c(0, 0)) +
  scale_y_continuous(expand = c(0, 0)) +
  labs(x = "Confidence", y = "") +
  scale_colour_flat_d(guide="none")

p2 <- estimate_density(df$RT, at=df$Participant, method = "kernSmooth") |> 
  ggplot(aes(x=x, y=y)) +
  geom_line(aes(color = Group)) +
  scale_x_continuous(expand = c(0, 0)) +
  scale_y_continuous(expand = c(0, 0)) +
  labs(x = "RT (s)", y = "") +
  scale_colour_viridis_d(guide="none")

p3 <- estimate_density(filter(df, !is.na(HeartRate)), select="HeartRate", at="Participant", method = "kernSmooth") |> 
  ggplot(aes(x=x, y=y)) +
  geom_line(aes(color = Participant)) +
  scale_x_continuous(expand = c(0, 0)) +
  scale_y_continuous(expand = c(0, 0)) +
  labs(x = "Heart Rate (bpm)", y = "") +
  scale_colour_pizza_d(guide="none")

p1 / p2 / p3 + plot_annotation(title = "Distribution of each participant")
```
## Theory of Mind / Empathy

### Yoni Task

```{r message=FALSE}
df %>% 
  group_by(Participant) %>% 
  select(starts_with("YONI_")) |> 
  summarise_all(mean, na.rm=TRUE) |> 
  tidyr::pivot_longer(-Participant, values_to = "Scores") |> 
  mutate(name = paste0(str_replace(name, "_", " ("), ")")) |> 
  ggplot(aes(x = Scores, fill = name)) +
  geom_density() +
  scale_fill_manual(values = c("YONI (Affective)" = "Purple",
                                 "YONI (Cognitive)" = "Blue",
                                 "YONI (Physical)" = "Green",
                                 "YONI (Total)"= "DarkBlue"),
                      guide = "none") +
  facet_wrap(~name, scales = "free")
```

### BES Questionnaire

```{r message=FALSE}
df %>% 
  group_by(Participant) %>% 
  select(starts_with("BES_")) |> 
  summarise_all(mean, na.rm=TRUE) |> 
  tidyr::pivot_longer(-Participant, values_to = "Scores") |> 
  mutate(name = paste0(str_replace(name, "_", " ("), ")")) |> 
  ggplot(aes(x = Scores, fill = name)) +
  geom_density() +
  scale_fill_manual(values = c("BES (Affective)" = "Purple",
                               "BES (Cognitive)" = "Blue",
                               "BES (Total)"= "DarkBlue"),
                      guide = "none") +
  facet_wrap(~name, scales = "free")
```

## Interoception

### Heartbeat Counting Task (HCT)

```{r message=FALSE}
df %>% 
  group_by(Participant) %>% 
  select(starts_with("HCT_")) |> 
  summarise_all(mean, na.rm=TRUE) |> 
  tidyr::pivot_longer(-Participant, values_to = "Scores") |> 
  mutate(name = paste0(str_replace(name, "_", " ("), ")")) |> 
  ggplot(aes(x = Scores, fill = name)) +
  geom_density() +
  scale_fill_manual(values = c("HCT (Accuracy)" = "Red",
                               "HCT (Awareness)" = "Orange",
                               "HCT (Confidence)"= "DarkOrange"),
                      guide = "none") +
  facet_wrap(~name, scales = "free")
```

### Heartbeat Tracking Task (HTT)

```{r message=FALSE}
htt_data <- read.csv("preprocessing/HTT_extracted.csv") |> 
  mutate(Condition = fct_recode(Condition, "NoGuessPerturbed" = "NoGuess_Perturbed")) |> 
  rename(Distance = Time_to_Rpeak) 

htt_data |>
  ggplot(aes(x = Distance, fill = Condition)) +
  geom_histogram(binwidth = 0.05, alpha = 0.5, position="identity") +
  geom_vline(xintercept = 0, linetype = "dashed") +
  facet_wrap(~ID) +
  see::theme_modern() 
```

### MAIA

```{r message=FALSE}
df %>% 
  group_by(Participant) %>% 
  select(starts_with("MAIA_")) |> 
  summarise_all(mean, na.rm=TRUE) |> 
  tidyr::pivot_longer(-Participant, values_to = "Scores") |> 
  mutate(name = paste0(str_replace(name, "_", " ("), ")")) |> 
  ggplot(aes(x = Scores, fill = name)) +
  geom_density() +
  scale_fill_brewer(palette = "Reds", guide = "none") +
  facet_wrap(~name, scales = "free")
```


## Deception

### LIE Scale

```{r message=FALSE}
df %>% 
  group_by(Participant) %>% 
  select(starts_with("LIE_")) |> 
  summarise_all(mean, na.rm=TRUE) |> 
  tidyr::pivot_longer(-Participant, values_to = "Scores") |> 
  mutate(name = paste0(str_replace(name, "_", " ("), ")")) |> 
  ggplot(aes(x = Scores, fill = name)) +
  geom_density() +
  scale_fill_manual(values = c("LIE (Ability)" = "#2196F3",
                               "LIE (Frequency)" = "#4CAF50",
                               "LIE (Contextuality)"= "#FF9800",
                               "LIE (Negativity)"= "#E91E63"),
                    guide = "none") +
  facet_wrap(~name, scales = "free")
```

### Deception Task

#### Physiological Processing

```{r warning=FALSE}
df_physio <- read.csv("preprocessing/deceptiontask_physio_extracted.csv") |> 
  dplyr::filter(ID != 30) |> 
  tidyr::pivot_longer(starts_with("X"), names_to = "Time", values_to = "HeartRate") |> 
  mutate(Time = as.numeric(str_remove(Time, "X"))-500,
         group = paste0(ID, condition, Answer),
         instruction = fct_relevel(Answer, "TRUTH")) |> 
  group_by(condition, Answer, Time) |> 
  summarise(HeartRate = mean(HeartRate)) |> 
  ungroup()
  
df_physio |> 
  ggplot(aes(x = Time, y = HeartRate)) +
  annotate("rect", xmin=1500, xmax=2500, ymin=-Inf, ymax=Inf, alpha=0.1, fill = "green") +
  geom_line(aes(color = condition, linetype = Answer), size=1) +
  geom_vline(aes(xintercept=0), linetype = "dotted") +
  labs(y = "Average Heart Rate (bpm)", x = "Time (ms)") +
  scale_color_manual(values = c("Polygraph" = "#FF5722", "Interrogation" = "#2196F3")) +
  theme(legend.position = "top", legend.title=element_blank())
```

#### Summary Table

```{r warning=FALSE}
df |> 
  group_by(Participant, Answer) |> 
  summarise(Confidence = paste(insight::format_value(mean(Confidence, na.rm = TRUE)),
                               " +- ",
                               insight::format_value(sd(Confidence, na.rm = TRUE))),
            RT = paste(insight::format_value(mean(RT, na.rm = TRUE)),
                       " +- ",
                       insight::format_value(sd(RT, na.rm = TRUE)))) |> 
  arrange(Participant) |> 
  knitr::kable()
```

#### Outliers

##### Participants

```{r warning=FALSE}
df |> 
  select(Participant, Confidence, RT, HeartRate) |> 
  tidyr::pivot_longer(-Participant) |> 
  ggplot(aes(x=Participant, y=value)) +
  geom_violin(aes(fill=name), color="white", alpha=0.5) +
  geom_jitter(aes(color=name), width = 0.25, height=0, shape="+", size=2) +
  facet_wrap(~name, scales="free", nrow=3) +
  guides(fill="none", color="none")
```



##### Observations


```{r warning=FALSE}
df |> 
  group_by(Participant) |> 
  summarise(Physio = sum(Outliers_RT) / n(),
            RT = sum(Outliers_Physio) / n()) |> 
  tidyr::pivot_longer(-Participant, names_to = "Outlier_Type") |> 
  ggplot(aes(x=Participant, y = value, fill = Outlier_Type)) +
  geom_bar(stat = "identity") + 
  scale_y_continuous(labels = scales::percent) + 
  labs(y = "Percentage of trials") +
  ggtitle("Number of Trial Dropped Per Participant")
  
df$RT[df$Outliers_RT] <- NA
df$HeartRate[df$Outliers_Physio] <- NA
```

#### Distributions

```{r warning=FALSE, fig.height=figheight*2}
p1 <- df |> 
  ggplot(aes(x = Confidence, fill = Participant)) +
  geom_density(alpha = 0.1) +
  see::scale_fill_material_d(palette = "rainbow", guide = "none") +
  scale_x_continuous(labels = scales::percent, expand=expansion(c(0, .05))) +
  scale_y_continuous(expand=expansion(c(0, .05))) +
  facet_wrap(~Answer)
p2 <- df |> 
  ggplot(aes(x = RT, fill = Participant)) +
  geom_density(alpha = 0.1) +
  see::scale_fill_material_d(palette = "rainbow", guide = "none") +
  scale_x_continuous(expand=expansion(c(0, .05))) +
  scale_y_continuous(expand=expansion(c(0, .05))) +
  facet_wrap(~Answer)
p3 <- df |> 
  ggplot(aes(x = HeartRate, fill = Participant)) +
  geom_density(alpha = 0.1) +
  see::scale_fill_material_d(palette = "rainbow", guide = "none") +
  scale_x_continuous(expand=expansion(c(0, .05))) +
  scale_y_continuous(expand=expansion(c(0, .05))) +
  facet_wrap(~Answer)
p1 / p2 / p3
```


## Validity and Reliability

### Lie Scale
```{r message= FALSE, warning=FALSE}
df<- read.csv('preprocessing/lie_processed.csv')
data.frame(Lie_Ability = 
               performance::cronbachs_alpha(
                   dplyr::select(df, Q4, Q5, Q6, Q7)),
           Lie_Negativity =
               performance::cronbachs_alpha(
                   dplyr::select(df, Q9, Q11, Q13, Q16,)),
           Lie_Frequency = 
               performance::cronbachs_alpha(
                    dplyr::select(df, Q1,Q2, Q3, Q8)),
           Lie_Contextuality = 
               performance::cronbachs_alpha(
                    dplyr::select(df, Q10, Q12, Q14, Q15)))

r<- correlation(select(df, LIE_Ability, LIE_Negativity, LIE_Frequency, LIE_Contextuality), p_adjust="none")
summary(r)|>
    plot()

```

### MAIA 
```{r message= FALSE, warning=FALSE}
df<- read.csv('preprocessing/MAIA2_processed.csv')
data.frame(MAIA_Noticing = 
               performance::cronbachs_alpha(
                   dplyr::select(df, Q1, Q2, Q3, Q4)),
           MAIA_NotDistracting =
               performance::cronbachs_alpha(
                   dplyr::select(df, Q5, Q6, Q7, Q8, Q9, Q10)),
           MAIA_NotWorrying = 
               performance::cronbachs_alpha(
                    dplyr::select(df, Q11,Q12, Q13, Q14, Q15)),
           MAIA_AttentionRegulation = 
               performance::cronbachs_alpha(
                    dplyr::select(df, Q16, Q17, Q18, Q19, Q20, Q21, Q22)),
           MAIA_EmotionalAwarness= 
               performance::cronbachs_alpha(
                   dplyr::select(df, Q23,Q24, Q25, Q26, Q27)),
           MAIA_SelfRegulation =
               performance::cronbachs_alpha(
                   dplyr::select(df, Q28, Q29, Q30, Q31)),
           MAIA_BodyListening = 
               performance::cronbachs_alpha(
                   dplyr::select(df, Q32, Q33, Q34)),
           MAIA_Trusting = 
               performance::cronbachs_alpha(
                   dplyr::select(df, Q35, Q36, Q37)
               ))

r<- correlation(select(df, starts_with('MAIA_')), p_adjust = "none")
summary(r)|>
    plot()

```

### BES
```{r message= FALSE, warning=FALSE}
df<- read.csv('preprocessing/BES_processed.csv')
data.frame(
    BES_Cognitve = 
        performance::cronbachs_alpha(
           dplyr::select(df, Q3, Q6, Q9, Q10, Q12, Q14, Q16, Q19, Q20)),
    BES_Affective =
        performance::cronbachs_alpha(
           dplyr::select(df, Q1, Q2, Q4, Q5, Q7, Q8, Q11, Q13, Q15, Q17, Q18)),
    BES_Total = performance::cronbachs_alpha(df)
        )

r_cog<- correlation(select(df, Q3, Q6, Q9, Q10, Q12, Q14, Q16, Q19, Q20, BES_Cognitive ), p_adjust="none")
r_aff<-correlation(select(df,  Q1, Q2, Q4, Q5, Q7, Q8, Q11, Q13, Q15, Q17, Q18, BES_Affective), p_adjust="none")

summary(r_cog)|>
    plot()

summary(r_aff)|>
    plot()

```

## Inter-Measures Correlation {.tabset}

```{r message=FALSE, warning=FALSE}
dfsub <- df |> 
  select(Participant, 
         starts_with("YONI_"), 
         starts_with("BES_"),
         starts_with("HCT_"),
         starts_with("HTT_"),
         starts_with("MAIA_"),
         starts_with("LIE_")) |> 
  group_by(Participant) |> 
  summarise_all(mean)
```

### Theory of Mind / Empathy

```{r message=FALSE, warning=FALSE}
r <- correlation(select(dfsub, starts_with("YONI_")),
                 select(dfsub, starts_with("BES_")), 
                 p_adjust = "none")

summary(r) |> 
  plot() 
```

### Interoception

```{r message=FALSE, warning=FALSE}
# Leave out HTT
# r <- correlation(select(dfsub, starts_with("HTT_")),
#                  select(dfsub, starts_with("HCT_")), 
#                  p_adjust = "none")
# 
# summary(r) |> 
#   plot()
```

```{r message=FALSE, warning=FALSE}
r <- correlation(select(dfsub, starts_with("MAIA_")),
                 select(dfsub, starts_with("HCT_")), 
                        #starts_with("HTT_")), 
                 p_adjust = "none")

summary(r) |> 
  plot()
```

### ToM and Interoception

```{r message=FALSE, warning=FALSE}
r <- correlation(select(dfsub, starts_with(c("MAIA_", "HCT_"))),
                 select(dfsub, starts_with(c("YONI_", "BES_"))), 
                 p_adjust = "none")

summary(r) |> 
  plot() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1, vjust = 1))
```

### Deception Task and LIE Scale

```{r message=FALSE, warning=FALSE}
r <- df |> 
  select(Participant, Answer, Confidence, RT, HeartRate) |> 
  group_by(Participant, Answer) |> 
  summarise_all(mean, na.rm=TRUE) |> 
  tidyr::pivot_wider(names_from = "Answer", values_from = c("Confidence", "RT", "HeartRate")) |> 
  ungroup() |> 
  select(-Participant) |> 
  correlation(select(dfsub, starts_with("LIE_")), p_adjust = "none")

summary(r) |> 
  plot()
```


### Confidence and RT

- When lying, the faster they answer, the more confident they are.

```{r message=FALSE, warning=FALSE}
model <- glmmTMB(Confidence ~ RT * Answer + (1|Participant) + (1|Item), 
                 data = df, family = beta_family())

parameters::parameters(model, effects = "fixed")
```

```{r message=FALSE, warning=FALSE}
modelbased::estimate_slopes(model, trend = "RT", at = "Answer")
```

```{r message=FALSE, warning=FALSE}
estimate_relation(model, at = c("RT", "Answer")) |> 
  plot(length = 50, point = list(alpha = 0.3, size = 3.5)) 
```

### Confidence and Heart Rate

- More confidence in truths is associated with higher heart rate.

```{r message=FALSE, warning=FALSE}
model <- glmmTMB(Confidence ~ HeartRate * Answer + (1|Participant) + (1|Item), 
                 data = df, family = beta_family()) # warning can be ignored

parameters::parameters(model, effects = "fixed")
```

```{r message=FALSE, warning=FALSE}
modelbased::estimate_slopes(model, trend = "HeartRate", at = "Answer")
```

```{r message=FALSE, warning=FALSE}
estimate_relation(model, at = c("HeartRate", "Answer")) |> 
  plot(length = 50, point = list(alpha = 0.3, size = 3.5)) 
```

### RT and Heart Rate

- No relationship.

```{r message=FALSE, warning=FALSE}
model <- glmmTMB(RT ~ HeartRate * Answer + (1|Participant) + (1|Item), 
                 data = df)

parameters::parameters(model, effects = "fixed")
```

```{r message=FALSE, warning=FALSE}
estimate_relation(model, at = c("HeartRate", "Answer")) |> 
  plot(length = 50, point = list(alpha = 0.3, size = 3.5)) 
```
